---
title: "Live Session 1 CLT"
author: "Taylor Bonar"
date: "01/05/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Simulator to Demonstrate CLT

## Control Parameters
```{r}
df = read.table("C:/Users/Taylo/Documents/SMU/MSDS-6306/MSDS_6306_Doing-Data-Science/Unit 5/yob2016.txt",stringsAsFactors = FALSE,header = FALSE,sep = ";")

n1 = 10 # sample size per sample for 1st distribution
n2 = 100 # sample size per sample for 2nd distribution (we will compare these distribuions) 
simulations = 1000 #number of samples and thus number of xbars we will generate.  
mu = 0; # mean parameter for use with normal distribuions
sigma = 1; # standard deviation parameter for use with normal distribuions
```

## Data Holder
```{r}
xbar_holder1 = numeric(simulations) # This will hold all the sample means for the first distribution.
xbar_holder2 = numeric(simulations) # This will hold all the sample means for the second distribution.
```

## Simulate and Store
Generate 1000 samples each of size 10 and find the mean of each sample.  Then store each mean in the xbar_holder vector.

```{r}
for (i in 1:simulations)
{ 
  sample1 = rnorm(n1,mean = mu, sd = sigma)
  sample2 = rnorm(n2,mean = mu, sd = sigma)
  xbar1 = mean(sample1)
  xbar2 = mean(sample2)
  xbar_holder1[i] = xbar1
  xbar_holder2[i] = xbar2
}
```

## display the distribution of sample means (plot a histogram of the sample means)
```{r}
par(mfrow = c(2,1))
hist(xbar_holder1, col = "blue", main = paste("Distribution of the sample mean: n = ", n1), xlab = "Dist 1 Sample Means", xlim = c(-4,4))
hist(xbar_holder2, col = "red", main = paste("Distribution of the sample mean: n = ", n2), xlab = "Dist 2 Sample Means", xlim = c(-4,4))
```

## summary statistics of the distribution of the simulated sample means. 
```{r}
summary(xbar_holder1) #5 number summary and the mean
summary(xbar_holder2) #5 number summary and the mean
sd(xbar_holder1) # standard deviation of dstribuion 1
sd(xbar_holder2) #standard deviation of distribuion 2

```

## 2.1 CLT -- Generate chi-squared distribution with a population of 10,000,000 with 2 degree of freedoms
```{r}
# Generate a set of random numbers following a chi distribution
observations = 10000000 # number of observations
rchi_df = 2 # degrees of freedom for rchisq
rchisq <- rchisq(observations, rchi_df)

length(rchisq) # Print length/size of rchisq vector
```
## 2.2 CLT -- Histogram demonstrating right-skewness of rchisq values
```{r}
# Use hist function to plot rchisq values 
hist(rchisq, breaks = 100000, main = "Right-Skewed Histogram of rchisq")
```

## 2.3 CLT -- Deriving population's mean and standard deviation
```{r}
mean(rchisq) # Calculate population's mean

sd(rchisq) # Calculate population's standard deviation
```

## 2.4 CLT -- Mean and Standard Deviation of Random Chi Distribution using Central Limit Theorem with Sample Size of 50
```{r}
# CLT for Sampling Distribution with Sample Means Size of 50
smallSampleSize <- 50 # Number of items to choose 

smallSampleMeans <- vector(mode = "numeric", simulations) # Creating empty vector for numeric objects with size of simulations (i.e. 1000)

for(i in 1:simulations) {
  smallSamples <- sample(rchisq, smallSampleSize) #Obtain samples from population based on desired sampling size
  smallSampleMeans[i] <- mean(smallSamples) #Calculate mean of gathered samples
}

# Sample Means Distributions' Mean sample size
mean(smallSampleMeans)

# Sample Means Distributions' Standard Deviation
sd(smallSampleMeans)
```

## 2.5 CLT -- Histogram of Central Limit Theorem with Sample Size of 10,000
```{r}
# CLT for Sampling Distribution with Sample Means Size of 10,000
largeSampleSize <- 10000 # Number of items to choose 

largeSampleMeans <- vector(mode = "numeric", simulations) # Creating empty vector for numeric objects with size of  simulations (i.e. 1000)

for(i in 1:simulations) {
  largeSamples <- sample(rchisq, largeSampleSize) #Obtain samples from population based on desired sampling size
  largeSampleMeans[i] <- mean(largeSamples) #Calculate mean of gathered samples
}
hist(largeSampleMeans, main = "Histogram of Sample Distribution of rchisq with Sample Size of 10,000", xlab = "Samples' Means")
```

## 2.6 CLT -- Mean and Standard Deviation of Random Chi Distribution using Central Limit Theorem with Sample Size of 10,000
```{r}
# Sample Means Distributions' Mean with sample size 10,000
mean(largeSampleMeans)

# Sample Means Distributions' Standard Deviation with sample size 10,000
sd(largeSampleMeans)
```